\plaintitle

### 2018-04-05 paper/paper.tex
...

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\small{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\small{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  When a user wants to ``make the room darker'',
  he should translate it to a real action like ``turn off the ceiling light''.
  To do so,
  he may have to ``toggle the wall switch''
  or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  If the user is a Chinese speaker, he might have to translate his intention
  % ``使房黒暗'' into ``make the room darker'',
  ``房間暗一点'' into ``make the room darker'',
  ``turn off the ceiling light'', 
  ``toggle the wall switch'',
  and finally to a command like ``\tt{\$ iot ceilinglight 0}''.

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in various situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \tt{git} commands
  from fragments of users' intentions.
\end{abstract}

@@

We propose a simple, flexible and powerful
command translation framework with which users can generate a complete
command string.
%
We provide a database consisting of
pairs of
(1) the description of the task that users want to perform,
and
(2) the actual command string required by the system.
(1) can be written using regular expressions in any language,

For example, the database can include data like
\tt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of ``\textit{translation paradigm}'' for
  generating a correct instruction to a machine from
  the user's vague intention
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item IME-like command etnry interface
% やりたいことを実行するインタフェース (IME的なもの)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

We implemented the ``{\GH}'' system
with which a user can translate his vague intention in various languages
into a complete \tt{git} command
using the {\EH} framework.

@@

We assume that the user is using \tt{bash} for his software
development activities.

@@

When the user wants to compare the latest \tt{README.md} file with an
older version, he tries to use \tt{git} to show the difference.
He may know that he can use the \tt{git diff} command to do the
conparison and invoke the following command like the following.

\begin{quotation}
\begin{verbatim}
$ git diff README.md
$
\end{verbatim}
\end{quotation}

Nothing happens, because this is not the approriate command
to compare the latest version of \tt{README.md}
with older versions.
%
More experienced user might use a command like the following,
but it does not show anything either, because the version specification
``\verb|HEAD^^|''
specifies a file included in the older ``commit'',
and the following command only compares the \tt{README.md}
with the with the file included in the last commit, where
\tt{README.md} might be the same as the latest version.

\begin{quotation}
  \verb|$ git diff HEAD^^ README.md|
\end{quotation}

If {\GH} is installed,
the user can type a special key (e.g. \tt{Cmd-Ctrl-G}) to invoke {\GH}
after typing ``\verb|git RE |'' to see how he can do the job.

\begin{figure}[h]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=10cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``README.mdをひとつ前のバージョンと比較する'',
which means that ``to compare README with the last verson.''
%
If the user thinks that that's what he wanted to do,
he can select the entry by moving the selection by typing arrow keys
and type the enter key.
Then the command line is replaced by the correct command string
that satisfies the user's need.

A description like ``1日前''(1 day ago) was also shown in the candidate list.
This means that the user can use the same string ``\tt{git RE 1}''
for getting the README.md file of the day before yesterday.
The command is ``\verb|$ git ... '@{1 days ago}|''.
Although such command options are very difficult to remember,
users can do the same thing only by saying \tt{RE} and \tt{1}.

@@

{\EH} search algorithm and database structure

@@

A powerful information retrieval mechanism ``{\EH}'' is used in {\GH}.

Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression which represents the help entry description
and a corresponding command pattern.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns are used for invoking commands or calling library functions
corresponding to the description.
%
For example, a help entry for finding a restaurant on the Web consists of
the following data:

\begin{quote}
  description: \\
  \stt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
  command: \\
  \stt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
\end{quote}

The first regular expression, the description part,
is for generating texts like
\qsf{Find a Chinese restaurant in San Francisco}, 
\qsf{Find a Chinese restaurant in Chicago}, etc.,
and the second part, command part,
is used to generate a command for accessing \tt{Yelp.com}.
In the first example, \qsf{Chinese} and \qsf{San Francisco}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a URL
\tt{http://www.yelp.com/search?find\_loc=San\%20Francisco\&find\_desc=Chinese}.

When the matched pattern like \qsf{San Francisco}
cannot be directly used in the command,
parameters for the command can be put after the description string,
separated by a TAB character.
For example, when a number like ``\tt{29247}'' should be used
for checking the
weather of San Francisco, we can describe the help entry like this:

\begin{quote}\small
 description: \\
 \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
 command: \\
 \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
\end{quote}

Here, selecting a menu entry \qsf{Check the weather of San Francisco}
will produce a command
\tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.

@@

First, the spec like \verb|#{file}| is expanded to a list of filenames like
\verb+README.md|Makefile|test.c+,
and the spec string becomes
``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
Then this regular expression is expanded to all the possible string that match this regexp like
\begin{verbatim}
delete a file README.md
remove a file README.md
delete a file Makefile
remove a file Makefile
...
\end{verbatim}

@@

If ``\verb|destroy|'' should also be used for the spec,
the spec can be modified to 
\verb+(delete|remove) a (#{file})+.

@@

\begin{verbatim}
  #{file}を(消す|消去する)
  /bin/rm $1
\end{verbatim}

@@

Regular expressions are widely used for finding patterns in text strings
in modern programming languages and in the Unix environment.
In {\EH}, we use regular expressions for
generating various patterns of descriptions in a short form.
For example, we use a short regular expression
\qtt{(remove|delete|erase) (data|file)}
for representing expressions like
\qsf{remove data},\qsf{erase file}, etc.

Converting a regular expression to a state transition machine is a straightforward task.
When we have a regular expression
\qtt{Find a (Chinese|Korean|Vietnamese) restaurant in (San Francisco|Chicago|New York) on Yelp.com}, 
we can parse the string and convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 573 124]{figures/statemachine.pdf}
\caption{State transition diagram for finding a restaurant.}
\label{statemachine1}
\end{figure}

@@

\begin{quote}
\small
\textsf{Find a Chinese restaurant in San Francisco} \\
\textsf{Find a Chinese restaurant in Chicago} \\
...\\
\textsf{Find a Vietnamese restaurant in New York}\\
\end{quote}

@@

We can generate texts from a state transition diagram by traversing nodes one by one.
Starting at the start node
(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
in Figure \ref{statemachine1},
we can visit other nodes via edges and generate a tree of generated texts
shown in Figure \ref{gentree1}.
After visiting the initial node
\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
the system generates a string \qsf{Find a} and proceeds to the next node.
In the second generation,
the system can add \qsf{Chinese}, \qsf{Korean}, and \qsf{Vietnamese}
to \qsf{Find a}, generating
\qsf{Find a Chinese}, \qsf{Find a Korean}, etc.
The system can repeat finding edges from previously visited nodes,
and eventually generates all the strings described above.
Of course, it is impossible to generate all the strings
from a regular expression like ``\tt{(0|1)+}'' which represents infinite length of
strings consisting of \tt{0}s and \tt{1}s, so the generation should be
terminated at certain generation.

@@

``Generate-and-test\footnote{
  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}''
technique is a simple and effective strategy
used for solving puzzles and AI problems.
For example,
the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

@@

Although usage examples are often shown on Unix man pages,
they cannot be used as the database of online help system.
On the other hand,
a {\SB} document contains both the manual page and the help database
at the same place.
%
This strategy is similar to the
``Literate Programming'' style,
where source codes and documents are put in the same document.

>>>>

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  %
  For example, when a Chinese person wants to ``房間暗一点'' (make the room darker),
  % he may have to translate his intention into an English expression ``make the room darker'',
  he may have to find that he should ``turn off the ceiling light'' for the task,
  translate it to a required action ``toggle the wall switch''
  or a command like ``\tt{\$ iot clight 0}''.
  %
  % When a user wants to ``make the room darker'',
  % he should translate it to a real action like ``turn off the ceiling light''.
  % To do so,
  % he may have to ``toggle the wall switch''
  % or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  % If the user is a Chinese speaker, he might have to translate his intention
  % ``房間暗一点'' into ``make the room darker'',
  % ``turn off the ceiling light'', 
  % ``toggle the wall switch'',
  % and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
  %
  There is a huge gap between ``房間暗'' and ``\tt{\$ iot clight 0}'', and
  people are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in various situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \tt{git} commands
  from fragments of users' intentions.
\end{abstract}

@@

We propose a simple, flexible and powerful
translation framework with which users can generate a complete
command string from fragments of users' vague intentions.
%
We provide a database consisting of pairs of
the description of the task that users want to perform (e.g. 房間暗一点)
and
the actual command string required by the system (e.g. \tt{\$ iot clight 0}).
Descriptions can be written in any natural language using regular expressions
and the database on the Wiki pages can be edited by any user
who wants to improve the database.

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of ``\textit{translation paradigm}'' for
  generating a correct instruction to an artifact from
  the user's vague intention in natural language.
\item General-purpose flexible dynamic search system based on regular expressions.
% そのための柔軟なインフラ (ExpandHelp)
% \item IME-like command etnry interface
% やりたいことを実行するインタフェース (IME的なもの)
\item Data sharing infrastructure for the above strategy.
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete \tt{git} command
using the {\EH} framework.

@@

We assume that the user uses \tt{bash} for his software
development activities.

@@

When a user wants to compare the latest \tt{README.md} file
with the same file from 2 versions before,
he might try to use \tt{git} with an argument
``\verb|HEAD^^|''
for specifying an old version.

\begin{quotation}
  \verb|$ git diff HEAD^^ README.md|
  \par
  \verb|$|
\end{quotation}

Nothing happens here because
\verb|HEAD^^|
specifies a file included in the older commit,
and the command above only compares the \tt{README.md}
with the file included in an old commit, where
\tt{README.md} might be the same as the latest version.

If {\GH} is installed,
the user can type a special shortcut key
% (e.g. \tt{Cmd-Ctrl-G})
to invoke {\GH} after typing ``\verb|git RE 2|'' to see how he can do the job.

\begin{figure}[h]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``README.mdをふたつ前のバージョンと比較する'',
which means ``to compare \tt{README.md} with the one from 2 versions before.''
%
If the user thinks that that's what he wants to do,
he can select the entry by selecting it by typing arrow keys
and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like ``2日前''(2 days ago) was also shown in the candidate list.
This means that the user can use the same string ``\tt{git RE 2}''
for getting the \tt{README.md} file of the day before yesterday.
The command,
``\verb|$ git diff '@{2 days ago}' README.md|'',
is difficult to remember,
but users can do the same thing only by saying \tt{RE} and \tt{2}.

A Japanese \tt{git} user can do the same thing just like
English-speaking users.

\begin{figure}[h]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash2}
\end{figure}

If the user wants to know more about the command line options,
he can click the ``i'' button and browse the Wiki page.
The page can be edited by any user, and

(Figure of Wiki here)

@@

% {\EH} search algorithm and database structure

@@

A flexible information retrieval mechanism ``{\EH}'' is used in {\GH}.

Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression that represents the help entry description
and a corresponding command pattern.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns are used for invoking commands or calling library functions
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be like this:

\begin{quote}
  description: \\
  \stt{Compare (\#{files}) with the one from (1|2|3|4) versions before}\\
  command: \\
  \stt{git diff ....}
\end{quote}

The first regular expression, the description part,
is for generating texts like
\qsf{Compare README.md with the one from 1 versions before}, 
\qsf{Compare index.html with the one from 2 versions before}, etc.,
and the second part, command part,
is used to generate a command to execute a \tt{git} command.
In the first example, \qsf{README.md} and \qsf{1}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a command
\tt{git xxxxxxx}.

% When the matched pattern like \qsf{San Francisco}
% cannot be directly used in the command,
% parameters for the command can be put after the description string,
% separated by a TAB character.
% For example, when a number like ``\tt{29247}'' should be used
% for checking the
% weather of San Francisco, we can describe the help entry like this:
% 
% \begin{quote}\small
%  description: \\
%  \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
%  command: \\
%  \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
% \end{quote}
%
% Here, selecting a menu entry \qsf{Check the weather of San Francisco}
% will produce a command
% \tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.

@@

First, the spec like \stt{\#\{file\}} is expanded to a list of filenames like
\verb+README.md|Makefile|test.c+,
and the spec string becomes
``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
Then this regular expression is expanded to all the possible string that match this regexp like
\begin{verbatim}
delete a file README.md
remove a file README.md
delete a file Makefile
remove a file Makefile
...
\end{verbatim}

@@

If ``\verb|destroy|'' should also be used for the spec,
the spec can be modified to 
\stt{(delete|remove) a (\#{file})}.

@@

\begin{verbatim}
  \#{file}を(消す|消去する)
  /bin/rm $1
\end{verbatim}

@@

Regular expressions are widely used for finding patterns in text strings
in modern programming languages and in the Unix environment.
In {\EH}, we use regular expressions for
generating various patterns of descriptions in a short form.
For example, we use a short regular expression
\sqtt{(remove|delete|erase) (data|file)}
for representing expressions like
\sqsf{remove data},\sqsf{erase file}, etc.

Converting a regular expression to a state transition machine is a straightforward task.
When we have a regular expression
\sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
we can parse the string and convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
\caption{State transition diagram for finding a restaurant.}
\label{statemachine1}
\end{figure}

@@

\begin{quote}
\small
\ssf{Compare README.md with the one 1 versions before} \\
\ssf{Compare index.html with the one 1 versions before} \\
...\\
\ssf{Compare package.json with the one 10 versions beforef}\\
\end{quote}

@@

We can generate texts from a state transition diagram by traversing nodes one by one.
Starting at the start node
(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
in Figure \ref{statemachine1},
we can visit other nodes via edges and generate a tree of generated texts
shown in Figure \ref{gentree1}.
After visiting the initial node
\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
the system generates a string \sqsf{Compare} and proceeds to the next node.
In the second generation,
the system can add \sqsf{README.md}, \sqsf{index.html}, and \sqsf{package.json}
to \sqsf{Compare}, generating
\sqsf{Compare README.md}, \sqsf{Compare index.html}, etc.
The system can repeat finding edges from previously visited nodes,
and eventually generates all the strings described above.
Of course, it is impossible to generate all the strings
from a regular expression like ``\tt{(0|1)+}'' that represents infinite length of
strings consisting of \tt{0}s and \tt{1}s, so the generation should be
terminated at certain generation.

@@

``Generate-and-test''\footnote{
  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}
is a simple and effective strategy
used for solving puzzles and AI problems.
For example,
the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

@@

Although usage examples are often shown on Unix man pages,
they cannot be used as the database of online help system.
On the other hand,
a {\SB} document contains both the manual page and the help database
at the same place.
%
This strategy is similar to the
``Literate Programming''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Literate\_programming}
} style,
where source codes and documents are put in the same document.
